Methodological details of the norming and production studies

### 2021-02-25 docs/methods_norm_prod/methods_norm_prod.tex
:bento: - upload methods description to the OSF

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Production study: Methodological details},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{expex}
\lingset{everygla=,everyglpreamble=\it}
\usepackage[export]{adjustbox}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Production study: Methodological details}
\author{}
\date{\vspace{-2.5em}9/17/2020}

@@

This document describes the methodological details of the production study, which generated the data your team will analyze for the \emph{Many Speech Analyses} project.

Although the details of the norming study (run prior to the production study, see OSF Wiki) might not be directly relevant for your analysis, we provide an outline of the norming study methods in Appendix \ref{norming} for context.

\hypertarget{research-question}{%
\section{Research question}\label{research-question}}

This study investigated whether speakers modify speech to signal atypical referents.
Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like \emph{blue banana} is different from one with a typical referent such as \emph{yellow banana}.

\hypertarget{participants}{%
\section{Participants}\label{participants}}

\hypertarget{procedure}{%
\section{Procedure}\label{procedure}}

In this production study, participants interacted with the experimenter in German.
Participants were seated in front of a computer screen.
The experimenter sat at the opposite side of the table in front of another computer screen.
The participants and the experimenter could not see each other nor each others' screens.
The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
The non-target objects differed from the target with respect to their color, their identity, or both.
Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
These color-object combinations differed with respect to their typicality.
The color-object combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix \ref{norming} for details).
Figure \ref{fig:image0} illustrates combination typicality for a banana, a tomato, and an apricot.

{\centering \includegraphics[width=0.6\linewidth]{typicality_examples}

{\centering \includegraphics[width=0.6\linewidth,frame]{sample_experiment_screen_competitor}

{\centering \includegraphics[width=0.6\linewidth,frame]{sample_experiment_screen_target}

\hypertarget{norming}{%
\section{Norming study}\label{norming}}

Here we specify in detail the selection of the stimuli for the production study.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Methodological details of the norming and production studies},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{expex}
\lingset{everygla=,everyglpreamble=\it}
\usepackage[export]{adjustbox}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Methodological details of the norming and production studies}
\author{}
\date{\vspace{-2.5em}9/17/2020}

@@

This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the \emph{Many Speech Analyses} project.

The norming study was run to obtain ratings on the typicality of color/object combinations used to create the experimental categories manipulated in the production study.
The production study then investigated whether speakers modify speech to signal the (a)typicality of the color/object combinations.
Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like \emph{blue banana} is different from one with a typical referent such as \emph{yellow banana}.

\hypertarget{norming-study}{%
\section{Norming study}\label{norming-study}}

Here we specify in detail the selection of the stimuli used in the production study.

@@

\hypertarget{production-study}{%
\section{Production study}\label{production-study}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

In this production study, participants interacted with the experimenter in German.
Participants were seated in front of a computer screen.
The experimenter sat at the opposite side of the table in front of another computer screen.
The participants and the experimenter could not see each other nor each others' screens.
The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
The non-target objects differed from the target with respect to their color, their identity, or both.
Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
These color-object combinations differed with respect to their typicality.
The color-object combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
Figure \ref{fig:image0} illustrates combination typicality for a banana, a tomato, and an apricot.

{\centering \includegraphics[width=0.6\linewidth]{/Users/ste/repos/many_analyses/figs/typicality_examples}

{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many_analyses/figs/sample_experiment_screen_competitor}

{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many_analyses/figs/sample_experiment_screen_target}
